Overview

### 2023-12-22 analysis/001_overview.Rmd
Update data to 0.2.91
Improve OECD ananlysi, in particular counting method!

ta_oa_inst <- readr::read_csv(here::here("data", "ta_oa_inst.csv.gz"))
```

@@

country_bar <- country_scatter_df |>
  group_by(cr_year, cat) |>
  summarise(all = sum(all), oa = sum(oa), ta_oa = sum(ta_oa)) |>
  mutate(closed = all - oa) |>
  pivot_longer(cols = c(oa, ta_oa, closed), names_to = "oa_type") |>
  ggplot(aes(gsub("^20", "'", as.character(cr_year)), value, group = oa_type, fill = oa_type)) +
  geom_area() +
  facet_wrap(~ cat) +
  scale_fill_manual(NULL, values = c(oa = "#b3b3b3a0", ta_oa = "#56B4E9", closed = "#e98b56"),
    labels = c(oa = "OA", ta_oa = "Agreement", closed = "Closed")) +
  theme_minimal() +
  scale_y_continuous(labels =  scales::number_format(big.mark = ",")) +
  theme_minimal() +
  labs(x = "Publication year", y = "Total articles") +
  theme(legend.position = "top",
    legend.justification = "left",
    legend.direction = "horizontal")
```

>>>>

ta_oa_inst <- readr::read_csv(here::here("data", "ta_oa_inst.csv.gz"))

@@

oecd_stats <- readr::read_csv(here::here("data", "oecd_stats.csv"))
oecd_stats_df <- oecd_stats |>
  filter(issn_l != "0027-8424", !cr_year %in%  c("2017", "2023")) |>
  filter(issn_l %in% hoaddata::cc_articles$issn_l) |>
  group_by(cr_year, cat) |>
  summarise(all = sum(articles, na.rm = TRUE), oa = sum(oa,na.rm = TRUE), ta_oa = sum(ta_oa, na.rm = TRUE)) |>
  mutate(closed = all - oa,
         oa_other = oa - ta_oa) |>
  pivot_longer(cols = c(ta_oa, oa_other, closed), names_to = "oa_type") |>
  mutate(cat = ifelse(is.na(cat), "Other", cat))

country_bar <- ggplot(oecd_stats_df, aes(gsub("^20", "'", as.character(cr_year)), value, group = oa_type, fill = oa_type)) +
  geom_area() +
  facet_wrap(~ cat) +
  scale_fill_manual(NULL, values = c(oa_other = "#b3b3b3a0", ta_oa = "#56B4E9", closed = "grey50"),
                    labels = c(oa_other = "OA Other", ta_oa = "Agreement", closed = "Closed")) +
  theme_minimal() +
  scale_y_continuous(labels =  scales::number_format(big.mark = ",")) +
  theme_minimal() +
  labs(x = "Publication year", y = "Total articles") +
  theme(legend.position = "top",
        legend.justification = "left",
        legend.direction = "horizontal")
